A note on the instability and degeneracy of deep learning models

### 2016-10-06 writing/note.Rmd
restructure from Nordman

# Discrete Expanding Finite space models and notions of instability

@@

To quantify "instability" in a model with discrete outcomes, it is useful to imagine how a data model might be expanded to incorporate more and more observations. A relevant quantity to this end is a (scaled) extremal log-probability ratio given by 
\begin{align}
\frac{1}{N} \log \left[\frac{\max\limits_{(x_1, \dots, x_N) \in \mathcal{X}^N}P_{\boldsymbol \theta_N}(x_1, \dots, x_N)}{\min\limits_{(x_1, \dots, x_N) \in \mathcal{X}^N}P_{\boldsymbol \theta}(x_1, \dots, x_N)}\right] \equiv \frac{1}{V} \text{ELPR}_N(\boldsymbol \theta_N) \label{eqn:elpr}
\end{align}

@@

Note this somewhat general result can be applied to many model families. In Section \ref{examples-of-def-models}, we present two specific examples of DEF models, including models with deep architectures.

# Examples of DEF models

>>>>

# Discrete Expanding Finite space models

@@

Note many model families can fall under the umbrella of DEF models. In Sections \ref{discrete-exponential-family-models}-\ref{deep-learning}, we present three specific examples of DEF models, including models with deep architectures.

# Instability and degeneracy results

To quantify "instability" in a model with discrete outcomes, it is useful to imagine how a data model might be expanded to incorporate more and more observations. A relevant quantity to this end is a (scaled) extremal log-probability ratio given by 
\begin{align}
\frac{1}{N} \log \left[\frac{\max\limits_{(x_1, \dots, x_N) \in \mathcal{X}^N}P_{\boldsymbol \theta_N}(x_1, \dots, x_N)}{\min\limits_{(x_1, \dots, x_N) \in \mathcal{X}^N}P_{\boldsymbol \theta}(x_1, \dots, x_N)}\right] \equiv \frac{1}{N} \text{ELPR}_N(\boldsymbol \theta_N) \label{eqn:elpr}
\end{align}

@@
